### 2018-04-29 paper/evaluation.tex

\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
}

@@

\end{figure}

% subsubsection simulating_user_behavior (end)

% subsection evaluation_testbed (end)

>>>>

\caption{\label{fig:sample_usage}Sample device usages using the previous HMM specifications. 
%The bottom line reads the HMM's states: \textbf{W}ork, \textbf{O}utside, and \textbf{H}ome, while the dark lines read when the devices (\textbf{h}ome computer, \textbf{p}hone, and \textbf{w}orkstation) are online.
}
\end{figure}

@@

\subsection{Predictive Onion Routes creation} % (fold)
\label{sub:predictive_onion_routes_creation}

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of Predictive Onion Route as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). We see that the number of nodes exponentially decreases a we relax the $\theta$ constraint.}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/success_rate_vs_t.pdf}
\caption{\label{fig:success_rate_vs_t}Availability rate of routes as a function of the time since the route establishment, for several values of the parameters $\theta$ (the maximal probability that all nodes in a layer fail at once) and $L$ (the number of layers in the route).}
\end{figure}
